---
title: "Organization Report Template"
subtitle: "Theme preview"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: !expr source("org_theme.R")$value
    toc: true
    toc_float: true
    df_print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
source("org_theme.R")
```

```{r, echo=FALSE}
htmltools::img(src ="logo.jpg",
               alt = 'logo',
               style = 'position:absolute; top:0; right:0; padding:10px;',
               width = "200px",
               heigth = "200px")
```

# Heading One

This is body text demonstrating the base font, color, and link styling —
[here is a link](https://example.com) to check the link colors.

## Heading Two

> This is a blockquote, styled with the Marigold accent border and a
> light grey background.

### Heading Three

Inline `code` and a fenced code block:

```r
summary(mtcars)
```

## Table

```{r}
knitr::kable(head(mtcars))
```

## Chart using the categorical brand palette

```{r,colours}

library("scales")
show_col(org_palette)
show_col(org_pal)
show_col(org_palette_categorical)
show_col(org_palette_extended)
show_col(org_palette_sequential_blueberry)

```

```{r}
library(ggplot2)

ggplot(mpg, aes(class, fill = class)) +
  geom_bar() +
  scale_fill_manual(values = org_pal(length(unique(mpg$class)))) +
  theme_minimal(base_family = "sans") +
  labs(title = "Vehicles by Class", x = NULL, y = "Count") +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1))
```

## Session Information

```{r,sessioninfo}

sessionInfo()

```

## Buttons / callouts (Bootstrap classes)

<button type="button" class="btn btn-primary">Primary</button>
<button type="button" class="btn btn-secondary">Secondary</button>
<button type="button" class="btn btn-success">Success</button>
<button type="button" class="btn btn-info">Info</button>
<button type="button" class="btn btn-warning">Warning</button>
<button type="button" class="btn btn-danger">Danger</button>
<br>
<hr>
*I acknowledge the Traditional Custodians of the land on which I live and work, and pay my respects to Elders, past and present.*
